---
title: "PRE VR5-KET Last 3 Days Acquisition"
author: "Jonathan Ramos"
date: "2024-04-12"
output: pdf_document
---

```{r}
library(ggplot2)
library(ggpubr)
library(car)
library(emmeans)
library(stringr)
library(rstatix)
```

# Acquisition 3way Repeated Measures ANOVA

I took these data from the prism file called "KETAMINE_BEHAVIOR_ALL.prism". In particular I created an aggregated csv with the data in long form (rather than wide form) from the following sheets:

  * 6 mg/kg Acquisition Last 3 days (ALPs)
  * 6 mg/kg Acquisition Last 3 days (ILPs) 
  * 6 mg/kg Acquisition Last 3 days (Rewards) 

In this markdown file I will perform three reactivation by treatment by day (2 x 2 x 3) repeated measures 3way ANOVAs; one each for active lever presses (ALP), inactive lever presses (ILP), and rewards. The Greenhouse Geisser correction is applied in all cases.

(None of the ANOVAs have any significant main or interaction effects)

```{r}
l3d <- read.csv('PRE-VR5_Last3Days_Acquisition.csv', sep = ',', header = TRUE)
l3d$day_factor <- as.factor(l3d$Day)
l3d$react_factor <- as.factor(l3d$React)
l3d$treat_factor <- as.factor(l3d$Treat)
l3d$rat_factor <- as.factor(l3d$Rat_n)
str(l3d)
```

## Active Lever Preses (ALP)
```{r}
res.aov <- anova_test(
  data = l3d, dv = ALP, wid = rat_factor,
  within = c(day_factor), between = c(treat_factor, react_factor)
  )
get_anova_table(res.aov, correction = 'GG')

res.aov
```

## Inactive Lever Preses (ILP)
```{r}
res.aov <- anova_test(
  data = l3d, dv = ILP, wid = rat_factor,
  within = c(day_factor), between = c(treat_factor, react_factor)
  )
get_anova_table(res.aov, correction = 'GG')

res.aov
```

## Rewards
```{r}
res.aov <- anova_test(
  data = l3d, dv = Rewards, wid = rat_factor,
  within = c(day_factor), between = c(treat_factor, react_factor)
  )
get_anova_table(res.aov, correction = 'GG')

res.aov
```